---
title: "README"
author: "Richard Cotton"
date: "2017-09-18"
output: md_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# githunt: An R package to get the email address from a github username

Trawl a github user's public events data for their email address.

## Installation

First, install the devtools package

```r
install.packages("devtools")
```

Then install this

```r
devtools::install_github("richierocks/githunt")
```

## Usage

The only function is `get_email_addresses()`, which takes a github username as its only argument.

```{r}
library(githunt)
get_email_addresses("richierocks")
```

## Isn't this creepy?

Yes, a little. Please use the package responsibly.

github stores a lot of data about your activities on public repositories. See

```
https://api.github.com/users/your-github-username/events/public
```

for what is being stored about yourself.

If you are concerned about your email address being made public, you can learn how to keep your email address private in the [GitHub documentation](https://help.github.com/articles/about-commit-email-addresses/).
